Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-12 paper.qmd
Changed the bin density for two_curvy

algo_obj_two_curvy <- fit_highd_model(
  highd_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  bin1 = num_bins_x_two_curvy, 
  q = 0.1, 
  benchmark_highdens = 5)

>>>>

algo_obj_two_curvy <- fit_highd_model(
  highd_data = training_data_two_curvy, 
  nldr_data = tsne_two_curvy, 
  bin1 = num_bins_x_two_curvy, 
  q = 0.1, 
  benchmark_highdens = 1)
